### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/canonicalize.tex
first complete review of the section 4

Now, we are ready to reconstruct the \fcanonicalize rule. This inference rule
defined in \eqref{eq:canonicalize} performs normalization for a proposition.
That is, depending on the role of the formula in the problem, it converts that
formula to its negative normal form or its conjunctive normal form. In both
cases, \canonicalize simplifies the formula by removing tautologies inside of
it as we widely described above for theorems in Fig.~\ref{fig:redundancies}.

Based on the \Metis source code, when the formula plays the axiom or
definition role, the \canonicalize rule transforms the source formula
to its negative normal form. Otherwise, this rule converts the
formula to a simplified conjunctive normal form.

Since this rule mostly consists of dealing with clauses, to
reconstruct this rule, our strategy mainly consists of checking the
equality of negative normal form between the source and the target
formula. If it fails, we try to reorder the conjunctive normal form
of the source formula to match with the conjunctive normal form of
the target formula. It definition is as follows.

>>>>

Now, we are ready to reconstruct the \fcanonicalize rule. This inference rule
defined in \eqref{eq:canonicalize} performs normalization for a proposition.
That is, depending on the role of the formula in the problem, it converts the
formula to its negative normal form or its conjunctive normal form. In both
cases, the \canonicalize rule simplifies the formula by removing tautologies
inside of it.

### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/clausify.tex
[ paper ] removed many examples and extra content.
[ pubs ] preparation of the paper (#60)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp

The \clausify rule is a rule that transforms a formula into
its clausal normal form but without performing simplifications of
tautologies. Recall, this kind of conversion was already
addressed by the \canonicalize rule. It is important to notice that
this kind of conversions between one formula to its clausal normal
form are not unique, and \Metis has customized approaches to perform
that transformations. Therefore, we perform a reordering of the
conjunctive normal form given by the $\fcnf$ function defined in
Lemma~\ref{lem:cnf} with the $\freorder_{∧∨}$ function from
Lemma~\ref{lem:reorder-and-or} to the input formula of the rule.

\begin{myexamplenum}
In the following \TSTP derivation by \Metis, we see how
\clausify transforms the \texttt{n₀} formula to get \texttt{n₁} formula.

@@

\begin{mainth}
\label{thm:clausify}
   Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ ⊢ \fclausify~φ~ψ$, where
  \begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fclausify : \Source → \Target → \Prop\\
  &\begin{array}{llll}
  \fclausify~φ~ψ &=
         \begin{cases}
        ψ, &\text{ if }φ≡ψ;\\
        \freorder_{∧∨}~(\fcnf~φ)~ψ, &\text{ otherwise.}
      \end{cases}
  \end{array}
  \end{aligned}
  \end{equation*}
\end{mainth}

\begin{proof}
If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma. Otherwise, we use Lemma~\ref{lem:reorder-and-or} and Lemma~\ref{lem:cnf}.
\end{proof}

>>>>

The \clausify rule is a rule that transforms a formula into its clausal normal
form but without performing simplifications of tautologies. Recall, this kind of
conversion was already addressed by the \canonicalize rule. It is important to
notice that this kind of conversions between one formula to its clausal normal
form are not unique, and \Metis has customized approaches to perform such
transformations.

To address the reconstruction of this rule, we perform a
reordering of the conjunctive normal form given by the $\fcnf$ function defined
in Lemma~\ref{lem:cnf} with the aforementioned function  $\freorder_{∧∨}$ to the
input formula of the rule.

\begin{myexamplenum} In the following \TSTP derivation by \Metis, the \clausify
rule transforms the \texttt{n₀} formula to get the \texttt{n₁} formula, that is
just the application of the distribution laws.

@@

\begin{mainth}
\label{thm:clausify}
   Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ ⊢ \fclausify~φ~ψ$, where
  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fclausify : \Source → \Target → \Prop\\
  &\begin{array}{llll}
  \fclausify~φ~ψ &=
         \begin{cases}
        ψ, &\text{ if }φ≡ψ;\\
        \freorder_{∧∨}~(\fcnf~φ)~ψ, &\text{ otherwise.}
      \end{cases}
  \end{array}
  \end{aligned}
  \end{empheq}
\end{mainth}

### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/simplify.tex
Nice box color for equations about functions
first complete review of the section 4

The \simplify rule is an inference that performs simplification of
tautologies in a list of derivations. This rule simplifies such a list
by transversing the list while applying Lemma~\ref{lem:canon-or},
Lemma~\ref{lem:canon-and}, among others theorems presented in the following.
The goal of this rule despites simplifying the list of derivations to a
new formula (often smaller than its input formulas), consists of finding
a contradiction.

@@

Since the main purpose of the \simplify rule is simplification of
formulas, we have defined the $\freduce$ function to help removing
the negation of a given literal $ℓ$ from a input formula.

\begin{equation}
\label{def:remove-literal}
  \begin{aligned}
  &\hspace{.495mm}\freduce : \Prop → \Lit → \Prop\hspace*{3.5cm}\\
  &\begin{array}{lll}
\freduce &(φ₁~∧~φ₂) &ℓ~= \fsimplify_{∧}~(\freduce~φ₁~ℓ~∧~\freduce~φ₂~ℓ)\\
\freduce &(φ₁~∨~φ₂) &ℓ~= \fsimplify_{∨}~(\freduce~φ₁~ℓ~∨~\freduce~φ₂~ℓ)\\[2mm]
\freduce &φ &ℓ~=\begin{cases}
  ⊥,  &\text{ if }φ\text{ is a literal and }ℓ ≡ \fnnf(¬ φ);\\
  φ,  &\text{ otherwise.}
  \end{cases}
   \end{array}
  \end{aligned}
\end{equation}

@@

The \fsimplify function is defined in~\eqref{eq:simplify}. If some
input formula is equal to the target formula, we derive that formula.
If some formula is $⊥$, we derive the target formula by using the
⊥-elim inference rule.
Otherwise, we proceed by cases on the structure of the formula.
For example, when the second source formula is a literal, we
use the $\freduce$ function and Lemma~\ref{lem:reduce-literal}.

\begin{equation}
\label{eq:simplify}
  \begin{aligned}
  &\hspace{.495mm}\fsimplify : \Source → \Source → \Target → \Prop \hspace*{3.5cm}\\
  &\begin{array}{l}
  \fsimplify~φ₁~φ₂~ψ~=\\
  \hspace{3mm}\begin{cases}
  ψ, &\text{ if }φᵢ ≡ ⊥\text{ for some }i = 1, 2;\\
  ψ, &\text{ if }φᵢ ≡ ψ\text{ for some }i = 1, 2;\\
  \fsimplify_{∧}~(\fsimplify~φ₁~φ₂₁~ψ)~φ₂₂~ψ,
  &\text{ if }φ₂ ≡ φ₂₁ ∧ φ₂₂;\\
   \fsimplify_{∨}~(\fsimplify~φ₁~φ₂₁~ψ~∨~\fsimplify~φ₁~φ₂₂~ψ)
  &\text{ if }φ₂ ≡ φ₂₁ ∨ φ₂₂;\\
  \freduce~φ₁~φ₂, &\text{ if }φ₂\text{ is a literal};\\
  φ₁,  &\text{ otherwise.}
  \end{cases}
  \end{array}
  \end{aligned}
\end{equation}

>>>>

The \simplify rule is an inference that performs simplification of tautologies
in a list of derivations. This rule simplifies such a list by transversing the
list while applying Lemma~\ref{lem:simplify-or}, Lemma~\ref{lem:simplify-and},
among others theorems presented in the following description. The goal of this
rule despites simplifying the list of derivations to a new formula (often
smaller than its input formulas), consists of finding a contradiction.

@@

Since the main purpose of the \simplify rule is to simplify formulas to get
$⊥$, we have defined the $\freduce$ function to help removing the negation
of a given literal $ℓ$ from a input formula.

\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
\label{def:remove-literal}
  \begin{aligned}
  &\hspace{.495mm}\freduce : \Prop → \Lit → \Prop\hspace*{3.5cm}\\
  &\begin{array}{lll}
\freduce &(φ₁~∧~φ₂) &ℓ~= \fsimplify_{∧}~(\freduce~φ₁~ℓ~∧~\freduce~φ₂~ℓ)\\
\freduce &(φ₁~∨~φ₂) &ℓ~= \fsimplify_{∨}~(\freduce~φ₁~ℓ~∨~\freduce~φ₂~ℓ)\\[2mm]
\freduce &φ &ℓ~=\begin{cases}
  ⊥,  &\text{ if }φ\text{ is a literal and }ℓ ≡ \fnnf(¬ φ);\\
  φ,  &\text{ otherwise.}
  \end{cases}
   \end{array}
  \end{aligned}
\end{empheq}

@@

The \fsimplify function is defined in~\eqref{eq:simplify}. If some
input formula is equal to the target formula, we derive that formula.
If any formula is $⊥$, we derive the target formula by using the
⊥-elim inference rule.
Otherwise, we proceed by cases on the structure of the formula.
For example, when the second source formula is a literal, we
use the $\freduce$ function and Lemma~\ref{lem:reduce-literal}.

\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
\label{eq:simplify}
  \begin{aligned}
  &\hspace{.495mm}\fsimplify : \Source → \Source → \Target → \Prop \hspace*{3.5cm}\\
  &\begin{array}{l}
  \fsimplify~φ₁~φ₂~ψ~=\\
  \hspace{3mm}\begin{cases}
  ψ, &\text{ if }φᵢ ≡ ⊥\text{ for some }i = 1, 2;\\
  ψ, &\text{ if }φᵢ ≡ ψ\text{ for some }i = 1, 2;\\
  \fsimplify_{∧}~(\fsimplify~φ₁~φ₂₁~ψ)~φ₂₂~ψ,
  &\text{ if }φ₂ ≡ φ₂₁ ∧ φ₂₂;\\
   \fsimplify_{∨}~(\fsimplify~φ₁~φ₂₁~ψ~∨~\fsimplify~φ₁~φ₂₂~ψ)
  &\text{ if }φ₂ ≡ φ₂₁ ∨ φ₂₂;\\
  \freduce~φ₁~φ₂, &\text{ if }φ₂\text{ is a literal};\\
  φ₁,  &\text{ otherwise.}
  \end{cases}
  \end{array}
  \end{aligned}
\end{empheq}
